Efficient UQ for chemical systems using active \author{Manav Vohra, Alen Alexanderian, Hayley Guy, Sankaran Mahadevan} subspaces

### 2018-08-13 Paper/method.tex
.

%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_as}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
\caption{Left: A bar-graph of activity scores ($\nu_{i,r}$'s) for the 19 uncertain pre-exponents ($A_i$'s); $r$
denotes the number of eigenvectors in the active subspace.
Right: A plot of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), defined as a normalized product of the
Poincare constant and the DGSM ($\mu_i$) (adapted from~\cite{Vohra:2018}).}
\label{fig:comp_as}
\end{center}
\end{figure}
%
The activity scores estimated using the two approaches agree favorably with each other as well as those
based on the screening metric involving the DGSMs from~\cite{Vohra:2018}. It is observed that the uncertainty
associated with the ignition delay is largely due to the uncertainty in $A_9$ and $A_1$. Sensitivity towards
$A_{15}$ and $A_{17}$ is also found to be significant.

The above comparisons establish consistency between gradient-based and
gradient-free approaches. Due to its reduced computational overhead, the
gradient-free approach is our method of choice for the 33-dimensional problem
in the next section.

>>>>

%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/comp_as}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
\caption{Left: A bar-graph of normalized activity scores ($\tilde{\nu_{i,r}}$'s) for the 19 uncertain pre-exponents ($A_i$'s); $r$
denotes the number of eigenvectors in the active subspace.
Right: A plot of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), defined as a normalized product of the
Poincare constant and the DGSM ($\mu_i$) (adapted from~\cite{Vohra:2018}).}
\label{fig:comp_as}
\end{center}
\end{figure}
%
The activity scores estimated using the two approaches agree favorably with each other as well as those
based on the screening metric involving the DGSMs from~\cite{Vohra:2018}. It is observed that the uncertainty
associated with the ignition delay is largely due to the uncertainty in $A_9$ and $A_1$. Sensitivity towards
$A_{15}$ and $A_{17}$ is also found to be significant.

The above comparisons establish consistency between gradient-based and
gradient-free approaches. This indicates that the local linear approximation
of the model output resulted in a reasonably accurate estimation of the
gradients in this case. In the following section, we will once again use both
approaches to discover an active subspace in the high-dimensional 
problem involving 33 uncertain inputs.
